Flatiron cleaning

### 2021-12-08 Rmd/rdi analysis.Rmd
Update rmd

```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  arrange(patientid, episodedate, drugname) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
  mutate(cycle_major_drugname = case_when(
    cycle_count_perline == drugname_count_perline &
      (drugname == "carboplatin" |
      drugname == "paclitaxel")                            ~ cycle_drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  # F01D908A013B7 has more pacli at the end but in the same line

@@

  mutate(line_keep = case_when(# F002B429BE6C6
    (linenumber_adj == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))            ~ "include"
  )) %>% 
  group_by(patientid) %>%
  fill(line_keep, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_treatment > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

@@

```{r RDI calculation}
RDI_data <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
```

@@

```{r Frontline_adjusted}
Frontline_adjusted <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
       .direction = "downup") %>% 
  ungroup() %>% 
  distinct(patientid, .keep_all = TRUE)
```

@@

study_criteria <- study_criteria %>%
  filter(line_keep == "include")
  # Remove patients with other linename
  # filter((linenumber_new == 1 &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin")) |
  #         (linenumber_new == 2 &
  #         therapy == "Upfront Chemo" &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin"))
  #        )
```

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
RDI_data <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)

RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
RDI_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(cycle_increment)) %>% 
  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```

Number of Adjuvant line in patients with upfront neo
```{r}
RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))

RDI_data %>% 
  filter(therapy == "Upfront Chemo") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
  arrange(desc(total_cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(total_cycle_increment) %>% 
  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
```
Number of Adjuvant line in patients with upfront surgery
```{r}
RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

RDI_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

## 2.Clinical Plots
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Age cat")+
  coord_flip()

@@

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Age cat")+
  coord_flip()

@@

<span style="color:green">**Table 3 Summary treatment data by race**</span>
```{r Table 3}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", "therapy"
           )) %>% 
  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

## 2.Treatment Plots
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>%
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(. ~ drugname)
```
</div>
</div>

@@

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10, fig.height=9}
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= name))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14)+
  coord_flip()
  # facet_wrap(. ~ therapy)

@@

<div class = "col-md-6">
```{r, fig.height=10, fig.height=9}
# Frontline %>% 
#   select(patientid, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj,
#          RDI_carbo_neo_grp, RDI_pacli_neo_grp, RDI_carbo_adj_grp, RDI_pacli_adj_grp) %>% 
#   pivot_longer(cols = -patientid, names_to = c("RDI", "group"), names_prefix = "_grp")
#   filter(!is.na(value)) %>% 
#   ggplot(aes(x= name))+
#   geom_bar(aes(fill = therapy, alpha = RDI_grp), position = position_dodge(preserve = "single"))+
#   theme_minimal(base_size = 14)+
  # coord_flip()
# 
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
#   # geom_boxplot()+
#   ylim(c(-.25, 2))+
#   geom_jitter(shape=16, aes(color=RDI_grp))+
#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
#   theme_minimal(base_size = 14) +
#   guides(color=FALSE)+
#   facet_wrap(.~ drugname, ncol = 2)
```
</div>
</div>

@@

```{r ggridges, fig.width=16, fig.height=18}
# library(ggridges)
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
#              )) +
#     geom_density_ridges(alpha=0.5) +
#     theme_ridges()+
#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 14)
#     ) +
#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
#   
#   facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
```

@@

<span style="color:green">**RDI summary table**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
  tbl_summary(by = therapy) %>% 
  bold_labels()

@@

@@

<span style="color:green">**Table 5 HR**</span>

## Univariable
```{r Table 5 HR}
# tbl2 <- Frontline %>%
#   filter(therapy == "Upfront Chemo")
# tbl1 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   add_
# tbl2 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl3 <- Frontline %>%
#   filter(therapy == "Upfront Surgery")
# tbl3 <- tbl3 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl5 <- tbl_merge(list(tbl2, tbl3))
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# 
# tbl_stack(list(tbl1, tbl5)) %>%
#   bold_labels() %>%
#   italicize_levels()

@@

```{r echo=FALSE, out.width='500%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```

>>>>

```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>% 
  arrange(patientid, episodedate, drugname) %>% 
  group_by(patientid, linenumber_new) %>%
  # Need the number of time of the "major" drug is seen in the line
  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
  mutate(cycle_major_drugname = case_when(
    cycle_count_perline == drugname_count_perline &
      (cycle_drugname == "carboplatin" |
      cycle_drugname == "paclitaxel")                      ~ cycle_drugname,
    TRUE                                                   ~ NA_character_
  )) %>% 
  # select(-drugname_count_perline) %>% 
  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
  # F01D908A013B7 has more pacli at the end but in the same line

@@

  mutate(line_keep = case_when(# F002B429BE6C6
    (linenumber_adj == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
    linenumber_adj == 1                                       ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(line_keep, .direction = "updown") %>% 
  ungroup() %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_treatment > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

@@

```{r RDI calculation}
Treatment <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup()

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
```

@@

```{r RDI_data}
RDI_data <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
       .direction = "downup") %>% 
  ungroup()
Frontline_adjusted <- RDI_data %>% 
  distinct(patientid, .keep_all = TRUE)
```

@@

study_criteria <- study_criteria %>%
  filter(is.na(line_keep))
  # Remove patients with other linename
  # filter((linenumber_new == 1 &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin")) |
  #         (linenumber_new == 2 &
  #         therapy == "Upfront Chemo" &
  #          (linename == "Carboplatin,Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
  #          linename == "Carboplatin" |
  #          linename == "Bevacizumab,Paclitaxel" |
  #          linename == "Paclitaxel" |
  #          linename == "Bevacizumab,Carboplatin"))
  #        )
```

@@

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

### Number of line /cycle received by patients in our study population

<span style="color:green">**Table supp 1 Number of total line**</span>
```{r}
full_data_study_pop %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new, therapy) %>% 
  tbl_summary(by = therapy)
```

<span style="color:green">**Table supp 1 Number of cycle in Neo**</span>
```{r}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary(type = list(cycle_increment ~ "continuous"))
```

<span style="color:green">**Table supp 1 Number of cycle in Adj**</span>
```{r}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, therapy) %>% 
  tbl_summary(by = therapy)
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(cycle_increment ~ "continuous"))
```
<br>

@@

<span style="color:green">**Table 3 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat")) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

## 2.Clinical Plots
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI Category at Diagnosis")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Age Category")+
  coord_flip()

@@

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category at Diagnosis")+
  coord_flip()

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Age Category")+
  coord_flip()

@@

<span style="color:green">**Table 4 Summary treatment data by race**</span>
```{r Table 4}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", "therapy"
           )) %>% 
  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,
           "debulking", "therapy"
           )) %>% 
  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

## 2.Treatment Plots
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>%
  ggplot(aes(x= bmi_cat, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>%
  ggplot(aes(x= bmi_cat, fill= debulking))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

full_data_study_pop %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  ggplot(aes(x= linename, fill= therapy))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14) + 
  facet_wrap(. ~ chemotherapy_type)+
  coord_flip()

full_data_study_pop %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  ggplot(aes(x= linename, fill= therapy))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14) + 
  facet_wrap(raceeth ~ chemotherapy_type)+
  coord_flip()

full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename, therapy) %>% 
  tbl_summary(by = therapy,
              label = list(linename ~ "line name received as Adjuvant"))
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>%
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>%
  ggplot(aes(x= debulking))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>%
  ggplot(aes(x= raceeth, fill= debulking))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

full_data_study_pop %>% 
  filter(linenumber_adj == 1) %>% 
  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
  ggplot(aes(x= linename, fill= therapy))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14) + 
  facet_wrap(bmi_cat ~ chemotherapy_type)+
  coord_flip()

full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  group_by(patientid, drugname) %>% 
  summarise(CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose)) %>% 
  ungroup() %>% 
  distinct(patientid, drugname, .keep_all = TRUE) %>% 
  select(CrCl, target_auc, expected_dose, drugname) %>% 
  tbl_summary(by = drugname,
              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
                           target_auc ~ "Target dose (AUC or mg/mg2)",
                           expected_dose ~ "Expected dose")
    )
```
</div>
</div>

@@

<div class = "row">
<div class = "col-md-6">
```{r rdi plots, fig.height=10, fig.height=9}
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= name))+
  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
  theme_minimal(base_size = 14)+
  coord_flip()

@@

<div class = "col-md-6">
```{r, fig.height=10, fig.height=9}
# Frontline %>%
#   select(patientid, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj,
#          RDI_carbo_neo_grp, RDI_pacli_neo_grp, RDI_carbo_adj_grp, RDI_pacli_adj_grp) %>%
#   pivot_longer(cols = -patientid, names_to = c("RDI", "group"), names_prefix = "_grp")
#   filter(!is.na(value)) %>%
#   ggplot(aes(x= name))+
#   geom_bar(aes(fill = therapy, alpha = RDI_grp), position = position_dodge(preserve = "single"))+
#   theme_minimal(base_size = 14)+
# coord_flip()
# 
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(x= name, y= value, color= value < 0.85))+
  geom_boxplot()+
  geom_jitter(shape=16)+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(.~ therapy, ncol = 2)
```
</div>
</div>

@@

```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=raceeth, x=value,  fill=raceeth
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+

  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")

Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=bmi_cat, x=value,  fill=bmi_cat
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+

  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")
```

@@

<span style="color:green">**RDI summary table**</span>

```{r}
my_theme <-
  list(
    # Some gt customization
    "as_gt-lst:addl_cmds" = list(
      # make the font size small
      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
                                                row.striping.include_stub = TRUE,
                                                row.striping.include_table_body = TRUE,
                                                row_group.border.top.color = "blue",
                                                # table.background.color = "white", 
                                                heading.background.color = "lightblue", 
                                                # column_labels.background.color = "orange", 
                                                row_group.background.color = "grey",
                                                stub.background.color = "slateblue", 
                                                summary_row.background.color = "tomato", 
                                                grand_summary_row.background.color = "green")),
      # add a custom title and subtitle to every table
      # user_added1 = rlang::expr(gt::tab_header(
      #   title = "Christelle's Table", subtitle = "Yeap"))#,
      # add a custom data source note
      # user_added2 = rlang::expr(gt::tab_source_note(
      #   source_note = "Source: our data!"))#,
      # stripe the table rows
      user_added1 = rlang::expr(gt::opt_row_striping())#,
      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
      )
    )

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)
trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt) %>%
  add_stat_label() %>%
  add_p() %>%
  as_gt() 
```

```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
  tbl_summary(by = therapy) %>% 
  bold_labels()

@@

```{r}
# reset_gtsummary_theme()
```

@@

<span style="color:green">**Table 6 HR**</span>

## Univariable
```{r Table 6 HR}
# tbl2 <- Frontline %>%
#   filter(therapy == "Upfront Chemo")
# tbl1 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   add_
# tbl2 <- tbl2 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl3 <- Frontline %>%
#   filter(therapy == "Upfront Surgery")
# tbl3 <- tbl3 %>%
#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
#   tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
# tbl5 <- tbl_merge(list(tbl2, tbl3))
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# 
# tbl_stack(list(tbl1, tbl5)) %>%
#   bold_labels() %>%
#   italicize_levels()

@@

```{r echo=FALSE, out.width='50%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```
